E Coli Project Paper Incredibly Rough Draft

### 2013-07-19 paper/paper.tex
more changes (these are not very good I need to go home)

\begin{document}
\title{E Coli project paper}

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}
\section{Introduction}
\subsection{What is the MinD system and why is it important?}
\subsection{How proteins move in cell}
\section{Methods and Initial Conditions}
The model for the behavior of the MinD and MinE proteins inside the cell
implemented the same set of 5 reaction-diffusion equations described in the paper
by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
were able to define a cell shape on the grid, and solve the
reaction-diffusion equations numerically to observe the time evolution of
the MinD and MinE concentrations inside the cell.

@@

%%Below are NOTES for the Writing

\section{Introduction}
It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.
They gneetically mutate the bacterial cells in order to eliminate certain proteins from them.  They eliminate MinC and SlmA.  SlmA deletion has very little effect accept for some assymetry in cell division area.  The MinC deletion shows a difference in volume division.  Only 73 percent divide with the approximate 1:1 ratio while for un deleted 99 percent do.This effect is seen in both flattened and unflattened cells, and its very similar in both, which is suprising.
Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior.  They use microfabricated silicon chips that have etched microchambers and shallow channels.

>>>>

\begin{document}
\title{E Coli Project Paper Incredibly Rough Draft}

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}
\section{Introduction}
\fixme{I need a lot of references here!!!  (And the writing is just terrible)}
It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.  The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.  One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.  This chain acts as a guide for the cell splitting process.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.

Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).

\subsection{What is the MinD system and why is it important?}
\subsection{How proteins move in cell}
\section{Methods and Initial Conditions}
The model for the behavior of the MinD and MinE proteins inside the cell
implemented the same set of 5 reaction-diffusion equations described in the paper
by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
were able to define a cell shape on the grid, and solve the
reaction-diffusion equations numerically to observe the time evolution of
the MinD and MinE concentrations inside the cell.

@@

\section{Below are NOTES for the Writing}

\section{Introduction}
\fixme{I need a lot of references here!!!}
It is vital that the process of bacterial cell division result in a single nucleiod in each daughter cell.  The cell must avoid minicelling, or splitting into daughter cells with lopsided volumes.  One of the mechanisms the cell employs in order to avoid this is to allow a long FtsZ polymer chain to develop on the cell wall in the center of the cell.  This chain acts as a guide for the cell splitting process.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein, which exhibits an aversion to the FtsZ polymer, from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.

Mannik et all have shown that the formation of irregular cell shapes adversly effects the Min system's ability to maintain their regular oscillatory behavior (cramming into spaces).
